---
title: About me
output:
    html_document:
        code_download: false
        toc: false
        number_sections: false
        code_folding: "none"
---

I'm an MD-PhD professional in bioinformatics with a medical degree from Acibadem University in 2015, postdoctoral experience at Yale University in 2016, followed by a PhD in Biostatistics and Bioinformatics in 2022. As of 2023, I've been working as a Bioinformatics Engineer at Genomics England, where I focus on maintaining and enhancing software for the cancer genomic medicine service.

My CV (PDF) is also available [here](./CV_doc/egeulgen_CV.pdf)

# Experience

```{r, echo=FALSE}
library(slickR)
library(htmltools)

generate_div <- function(role_and_company, years, description, logo_path) {
    description_div <- tags$div(
        tags$h3(role_and_company,
                style = css(color = "black")), 
        tags$div(
            tags$h4(years,
                    style = css(color = "black")), 
            tags$p(description,
                   style = css(color = "black"))
        )
    )
    
    d <- tags$div(
        style = css(display = "flex", "align-items" = "center"),
        tags$div(
            style = css(display = "flex", "flex-direction" = "column", "margin-right" = "20px", width = "20%"),
            tags$img(src=logo_path)
        ),
        tags$div(
            style = css(display = "flex", "flex-direction" = "column", "margin-right" = "20px", width = "80%", "text-align" = "left"), 
            description_div
        )
    )
    return(d)
}
```

```{r, echo=FALSE, out.height="200px"}
experiences <- slick_list(
    generate_div(
        role_and_company = "Bioinformatics Engineer - Genomics England",
        years = "2023-",
        description = "Developing features for and maintaining software for the cancer genomic medicine service.",
        logo_path = "images/Genomics_England_logo.svg"
    ),
    generate_div(
        role_and_company = "Lecturer - Acibadem University",
        years = "2021-2023",
        description = "Worked as a lecturer for the undergrad and grad courses on biostatistics and bioinformatics topics.",
        logo_path = "images/ACU_logo.png"
    ),
    generate_div(
        role_and_company = "Bioinformatics Specialist - Epigenetiks",
        years = "2018-2023",
        description = "Worked on developing and maintaining multiple whole exome sequencing-based analysis pipelines (cancer and rare disease applications) for the Istanbul-based medical diagnostics company.",
        logo_path = "images/epigenetiks_logo.png"
    ),
    generate_div(
        role_and_company = "Postdoctoral Associate - Yale University",
        years = "2016",
        description = "Briefly worked as a post-doc associate at the Gunel Lab, Yale School of Medicine, where I had previously done multiple internships between 2011-2014. Research in neurogenetics, particularly malformations of cortical development and brain tumours, performing functional in-vitro analyses to investigate the effect of a SNP in the pathogenesis of gliomas.",
        logo_path = "images/yale-logo.svg"
    ),
    generate_div(
        role_and_company = "Bioinformatics Consultant - NeuroOncology Technologies",
        years = "2015-2023",
        description = "Developed and maintained the Whole Exome Sequencing pipeline for the local medical diagnostics company based in Istanbul-Turkey. The pipeline allows for the identification of clinically-relevant genomics findings in brain tumours, especially regarding gliomas.",
        logo_path = "images/NOT_logo.svg"
    ),
    generate_div(
        role_and_company = "Research Group Member - ACU Brain tumour Research Group",
        years = "2012-",
        description = "Participate in research on brain tumours, particularly on gliomas. I assist in biostatistical as well as bioinformatics analyses, focusing on the integration of molecular biological and clinical data to improve diagnosis, prognosis and treatment of glioma.",
        logo_path = "images/AUBTRG_logo.svg"
    )
)

slickR(experiences) + 
    settings(dots = TRUE, adaptiveHeight = TRUE, draggable = TRUE, autoplay = TRUE, autoplaySpeed = 4000)
```

# Skills

```{r, echo=FALSE}
skill_rating <- function(skill, logo_fname, rating) {
    RATING_HEIGHT <- 15
    LOGO_HEIGHT <- 45
    rating_vec <- c(
        rep(as.character(img(src="images/raw/rating1.svg", height = RATING_HEIGHT)), rating), 
        rep(as.character(img(src="images/raw/rating0.svg", height = RATING_HEIGHT)), 3 - rating)
    )
    
    logo <- as.character(img(src=file.path("images/raw", logo_fname), alt = skill, height = LOGO_HEIGHT))
    
    result <- paste0("<table><tr><td>", logo, "</td></tr><tr><td>", paste(rating_vec, collapse = ""), "</td></tr></table>")
    result <- paste0('<div style="display: inline-block;margin-right: 20px;text-align: center;">', result, "</div>   ")
    return(result)
}
```

## Programming
`r skill_rating("Python", "Python-logo-notext.svg", 3)`
`r skill_rating("R", "Rlogo.svg", 3)` 
`r skill_rating("bash", "bash_logo.png", 2)`

## Development
`r skill_rating("git", "Git-Logo-2Color.svg", 2)`
`r skill_rating("docker", "docker_logo.svg", 1)`
`r skill_rating("PyCharm", "PyCharm_Icon.svg", 2)`
`r skill_rating("GitLab CI/CD", "gitlab-ci-cd.svg", 1)`
`r skill_rating("GitHub Actions", "githubactions.svg", 1)`

## Workflow Management
`r skill_rating("Nectflow", "nextflow-logo-bg-light.svg", 2)`
`r skill_rating("snakemake", "snakemake_logo.png", 2)`
