---
title: About me
output:
    html_document:
        code_download: false
        toc: false
        number_sections: false
        code_folding: "none"
---

I'm an MD-PhD professional in bioinformatics with a medical degree from Acibadem University in 2015, postdoctoral experience at Yale University in 2016, followed by a PhD in Biostatistics and Bioinformatics in 2022. Since 2023, I've been working as a Bioinformatics Engineer at Genomics England, where I focus on maintaining and enhancing software for the cancer genomic medicine service.

My CV (PDF) is also available [here](./CV_doc/egeulgen_CV.pdf)

# Experience

```{r, echo=FALSE}
source("utils.R")
```

```{r, echo=FALSE, out.height="200px"}
experiences <- slick_list(
    generate_div(
        header = "Bioinformatics Engineer - Genomics England",
        sub_header = "2023-",
        description = "Developing features for and maintaining software for the cancer genomic medicine service.",
        img_path = "images/Genomics_England_logo.svg"
    ),
    generate_div(
        header = "Lecturer - Acibadem University",
        sub_header = "2021-2023",
        description = "Worked as a lecturer for the undergrad and grad courses on biostatistics and bioinformatics topics.",
        img_path = "images/ACU_logo.png"
    ),
    generate_div(
        header = "Bioinformatics Specialist - Epigenetiks",
        sub_header = "2018-2023",
        description = "Worked on developing and maintaining multiple whole exome sequencing-based analysis pipelines (cancer and rare disease applications) for the Istanbul-based medical diagnostics company.",
        img_path = "images/epigenetiks_logo.png"
    ),
    generate_div(
        header = "Postdoctoral Associate - Yale University",
        sub_header = "2016",
        description = "Briefly worked as a post-doc associate at the Gunel Lab, Yale School of Medicine, where I had previously done multiple internships between 2011-2014. Research in neurogenetics, particularly malformations of cortical development and brain tumours, performing functional in-vitro analyses to investigate the effect of a SNP in the pathogenesis of gliomas.",
        img_path = "images/yale-logo.svg"
    ),
    generate_div(
        header = "Bioinformatics Consultant - NeuroOncology Technologies",
        sub_header = "2015-2023",
        description = "Developed and maintained the Whole Exome Sequencing pipeline for the local medical diagnostics company based in Istanbul-Turkey. The pipeline allows for the identification of clinically-relevant genomics findings in brain tumours, especially regarding gliomas.",
        img_path = "images/NOT_logo.svg"
    ),
    generate_div(
        header = "Research Group Member - ACU Brain tumour Research Group",
        sub_header = "2012-",
        description = "Participate in research on brain tumours, particularly on gliomas. I assist in biostatistical as well as bioinformatics analyses, focusing on the integration of molecular biological and clinical data to improve diagnosis, prognosis and treatment of glioma.",
        img_path = "images/AUBTRG_logo.svg"
    )
)

slickR(experiences) + 
    settings(dots = TRUE, adaptiveHeight = TRUE, draggable = TRUE, autoplay = TRUE, autoplaySpeed = 4000)
```
